\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-12 final/article.tex
fixed formatting by adding \ge and stuff

	We consider the tradeoff of with how many variables we represent a run and how tractable and verifiable our analysis is.  We considered a representation of n >= 4 dimensions, adding instantaneous parameters such as pace, heart rate, etc. and found that these additional parameters gave us little benefit while greatly complicating our analysis.  We found that variables time, distance elapsed, and total distance provided the simplest reasonable and most tractable effective results.\\

	To implement a k-nearest neighbors algorithm we had to make a best definition of nearest and determine how many neighbors to include in our analysis.  We considered other definitions of nearest but settled on comparing z-values as we assumed the invariant of good data and only comparing among the same runner such that many other variables can be ignored for the sake of our analysis.  We semi-arbitrarily came to the conclusion of using k=5 for our neighbors, determining that 5 strikes a nice balance between an accurate prediction, fast execution, and readable results.  We found that for k>=5 the quantitative benefit of additional neighbors dropped off exponentially.\\

>>>>

	We consider the tradeoff of with how many variables we represent a run and how tractable and verifiable our analysis is.  We considered a representation of n $\ge$ 4 dimensions, adding instantaneous parameters such as pace, heart rate, etc. and found that these additional parameters gave us little benefit while greatly complicating our analysis.  We found that variables time, distance elapsed, and total distance provided the simplest reasonable and most tractable effective results.\\

	To implement a k-nearest neighbors algorithm we had to make a best definition of nearest and determine how many neighbors to include in our analysis.  We considered other definitions of nearest but settled on comparing z-values as we assumed the invariant of good data and only comparing among the same runner such that many other variables can be ignored for the sake of our analysis.  We semi-arbitrarily came to the conclusion of using k=5 for our neighbors, determining that 5 strikes a nice balance between an accurate prediction, fast execution, and readable results.  We found that for k$\ge$5 the quantitative benefit of additional neighbors dropped off exponentially.\\
